### 2015-12-02 paper.tex
Move comment to issue #28

The mean velocity field at a tip speed ratio $\lambda=3.1$, 1 m downstream
($x/D=0.93$) is plotted in Fig.~\ref{fig:meancontquiv}. The mean streamwise
velocity deficit is markedly more symmetric than that of the UNH-RVAT, with
lower acceleration around the turbine thanks to lower rotor drag coefficient and
blockage ratio \cite{Bachant2015-JoT}. We also see that the effects of blade tip
vortex shedding are relatively weaker, which is likely an effect of the RM2's
lower solidity and tapered blades.\textbf{\textit{[the last 2 sentences: it's difficult to understand this without knowing the UNH-RVAT. Suggest to add a discussion on the similarity & differences between RVAT and RM2 dimensions, testing, and add the mean velocity plot for RVAT side-by-side with the one for RM2.  Need more details on how you see the effects of vortex shedding are weaker.]}}

>>>>

The mean velocity field at a tip speed ratio $\lambda=3.1$, 1 m downstream
($x/D=0.93$) is plotted in Fig.~\ref{fig:meancontquiv}. The mean streamwise
velocity deficit is markedly more symmetric than that of the UNH-RVAT, with
lower acceleration around the turbine thanks to lower rotor drag coefficient and
blockage ratio \cite{Bachant2015-JoT}. We also see that the effects of blade tip
vortex shedding are relatively weaker, which is likely an effect of the RM2's
lower solidity and tapered blades.
